---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oFDAinfo

<!-- badges: start -->
<!-- badges: end -->

The goal of oFDAinfo is to pull drug data from the [openFDA API](https://open.fda.gov/). I use it to find their package-NDC code, though there are many other uses. 

## Installation

This package relies heavily on the [openfda](https://github.com/ropenhealth/openfda), which must be installed prior to downloading oFDAinfo. You can install the development version of oFDAinfo from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ropenhealth/openfda")
devtools::install_github("jonahgorodensky/oFDAinfo")
```
## Example

At its most basic there is only one function of interest, `ndc_query`, which both pulls from the API and cleans the data into one dataframe. 
```{r example}
library(oFDAinfo)
## basic example code
drugs_of_interest <- list(c("generic_name", "methotrexate"), 
                          c("brand_name", "humira")
                          )
output <- ndc_query(drugs_of_interest,  csv = FALSE)
output
```

Assuming the same type (eg. generic_name or brand_name) it is equally possible to run `ndc_query(c("generic_name","drug1+drug2")` or `ndc_query(c("generic_name","drug1"), c("generic_name","drug2")`. Though the first is more concise I prefer the second as, although the outputs are equivalent, the ordering of the rows is more predictable when each drug is given its own call.
```{r}
first <- ndc_query(list(c("generic_name", "ibuprofen"), c("generic_name","ustekinumab")), csv = FALSE)
second <- ndc_query(list(c("generic_name", "ibuprofen+ustekinumab")), csv = FALSE)

dplyr::all_equal(first, second, ignore_row_order = TRUE)
dplyr::all_equal(first, second, ignore_row_order = FALSE)

```

